Supplementary data for: \\textit{`MSnbase`, efficient and elegant R-based processing and visualisation of raw mass spectrometry data}

### 2020-07-02 large_experiment_processing.Rmd
Update large_experiment_processing.Rmd
Co-authored-by: Sebastian Gibb <mail@sebastiangibb.de>

The `fromFile` function can be used to determine from which file (sample) a
specific spectrum in the `MSnExp` object is. This function returns an `integer`
vector, same length than spectra in the experiment, with the file index; the
file names can be accessed with the `fileNames` method. A `MSnExp` object can be
subsetted with `[` and e.g. the index of the spectra that should be retained. In
the code block below we subset our `ms_dsk` object to contain only spectra from
the 3rd file.

@@

Note that any of the data manipulations above are not directly applied to the
data but *cached* in the object's internal *lazy processing queue* (explaining
the very short running time of the normalization call). The operations are only
effectively applied to the data when m/z or intensity values are extracted from
the object as it is the case in the `plot` call above.

>>>>

The `fromFile` function can be used to determine the source file (sample)
specific spectrum in the `MSnExp` object is. This function returns an `integer`
vector, same length than spectra in the experiment, with the file index; the
file names can be accessed with the `fileNames` method. A `MSnExp` object can be
subsetted with `[` and e.g. the index of the spectra that should be retained. In
the code block below we subset our `ms_dsk` object to contain only spectra from
the 3rd file.

@@

Note that any of the data manipulations above are not directly applied to the
data but *cached* in the object's internal *lazy processing queue* (explaining
the very short running time of the normalization call). The operations are only
effectively applied to the data when m/z or intensity values are extracted from
the object, e.g. in the `plot` call above.
